InferentialStats

### 2018-03-07 E1/doInferentialStats.Rmd
good
moved prereg over to E2 folder

Print effect size
```{r}
leftBiasCanonical <- mean(   filter(all,dv=="efficacy" & orientation=="Canonical")$leftBias  )
leftBiasInverted<- mean(   filter(all,dv=="efficacy" & orientation=="Inverted")$leftBias  )
leftBiasDiff<- leftBiasCanonical - leftBiasInverted
```

The leftBiasDiff for this experiment is `r leftBiasDiff`, very healthy.

```{r, echo=FALSE}
P1E1canonical=.23
P1E1reversed= .062
P1E2canonical=.218 #sd=.034
P1E2inverted=.017 #sd=.049
```

What was it for the first paper? For E1,`r P1E1canonical`  Canonical and 
`r P1E1reversed` Mirror-reversed. Difference is `r P1E1canonical-P1E1reversed`

For E2, very similar at `r P1E2canonical - P1E2inverted`.

@@

http://jeffrouder.blogspot.com.au/2016/01/what-priors-should-i-use-part-i.html
For the null model, the bias is just zero (delta function).

For our model, support is zero to infinity. 
```{r}

#Specify alternative hypothesis (prior)

#Specify Alternative (up to constant of proportionality)
lo=0 #lower bound of support
hi=Inf #upper bound of support
altDens=function(delta) {
  y= dnorm(delta,.5,.3)
  y=y*as.integer(delta>lo)*as.integer(delta<hi) #multiply by zero if outside of support
}

#Normalize alternative density in case user does not, 
K=1/integrate(altDens,lower=lo,upper=hi)$value
f=function(delta) K*altDens(delta)

delta=seq(-2,3,.01)

#Plot Alternative as a density and Null as a point arrow
maxAlt=max(f(delta))
plot(delta,f(delta),typ='n',xlab="Effect Size Parameter Delta",ylab="Density",ylim=c(0,1.4*maxAlt),main="Models")
arrows(0,0,0,1.3*maxAlt,col='darkblue',lwd=2)
lines(delta,f(delta),col='darkgreen',lwd=2)
legend("topright",legend=c("Null","Alternative"),col=c('darkblue','darkgreen'),lwd=2)

@@

>>>>

Print effect size
```{r}
leftBiasesCanonical<- filter(all,dv=="efficacy" & orientation=="Canonical")$leftBias
leftBiasCanonical <- mean( leftBiasesCanonical )
leftBiasesInverted<- filter(all,dv=="efficacy" & orientation=="Inverted")$leftBias
leftBiasInverted<- mean(   leftBiasesInverted  )
leftBiasDiff<- leftBiasCanonical - leftBiasInverted
leftBias_sd <- sd(   leftBiasesCanonical - leftBiasesInverted )
```

The leftBiasDiff for this experiment is `r leftBiasDiff` or in Cohen's d `leftBiasDiff / leftBias_sd`, very healthy.

```{r, echo=FALSE}
E1n<- 16
#Raw effect size plus standard error and sd
P1E1canonical=.23;  P1E1c_se = .058; P1E1c_sd = P1E1c_se * sqrt(E1n)
P1E1reversed= .062;  P1E1r_se = .07; P1E1r_sd = P1E1r_se * sqrt(E1n)
#To calculate sd of the bias diff, consider that the variances sum,
#therefore first sum the variances then convert back to standard deviation
#Although only true for *independent* random variables and these unlikely to be totally independent
P1E1diff_sdCalculated = sqrt( (P1E1c_sd^2 + P1E1r_sd^2) )  #.257

E2n<- 24
P1E2canonical=.218; P1E2c_se =.034; P1E2c_sd= P1E2c_se * sqrt(E2n)
P1E2inverted=.017; P1E2i_se =.049; P1E2i_sd = P1E2i_se * sqrt(E2n)
P1E2diff_sdCalculated = sqrt( (P1E2c_sd^2 + P1E2i_sd^2) ) #.2066

P1E2vertUpright=.188; P1E2vu_se=.043; P1E2vu_sd = P1E2vu_se * sqrt(E2n)
P1E2vertInverted= -.07; P1E2vi_se=.049; P1E2vi_sd = P1E2vi_se * sqrt(E2n)
P1E2vdiff_sdCalculated = sqrt( (P1E2vi_sd^2 + P1E2vu_sd^2) )

P1E1leftBiasDiff<- P1E1canonical-P1E1reversed
P1E2leftBiasDiff<- P1E2canonical - P1E2inverted
P1E2vertBiasDiff<- P1E2vertUpright - P1E2vertInverted
#reported as  .258 +/- .047 in the paper

#The diff standard errors are also available from the paper directly. But still need to 
#convert to SD to get Cohen's d.

P1E1diff_se<-.07; P1E1diff_sd<- P1E1diff_se*sqrt(E2n) 
P1E2diff_se<-.038; P1E2diff_sd<- P1E2diff_se*sqrt(E2n) 
P1E2vdiff_se<- .047; P1E2vdiff_sd<- P1E2vdiff_se*sqrt(E2n)

What was it for the first paper? For E1,`r P1E1canonical`  Canonical and 
`r P1E1reversed` Mirror-reversed. Difference is `r P1E1canonical-P1E1reversed`
. For E2, bias difference very similar at `r P1E2leftBiasDiff`.
For E2 vertical arrangement, `r P1E2vertBiasDiff`

@@

Use the default Bayes test (but for E2 will use a custom prior)

```{r, echo=FALSE}
if(!require(BayesFactor)){install.packages('BayesFactor')}
library(BayesFactor)

leftBiasDifferences<- leftBiasesCanonical - leftBiasesInverted

ttestResults<- ttestBF( leftBiasDifferences )

@@

The Bayes factor from a one-sample default Bayes t-test for the leftBiasDifferences is `r ttestResults@bayesFactor$bf`

The full results are 
```r 
print(ttestResults)
```

A custom prior would provide more power, as detailed in bayesianAnalysisForPrereg.Rmd in E2 folder
